\textbf{\Large Computer Vision-based System for Impaired Human Vision Compensation}

### 2019-01-20 bare_conf.tex
Bibliography fixes according to reviews.

\bibitem{Bourne} Bourne RRA, Flaxman SR, Braithwaite T, Cicinelli MV, Das A, Jonas JB, et al.; Vision Loss Expert Group. Magnitude, temporal trends, and projections of the global prevalence of blindness and distance and near vision impairment: a systematic review and meta-analysis. Lancet Glob Health. Vol. 5(9), pp. 888-897, 2017.

\bibitem{Caraiman} Caraiman, S., Morar, A., Owczarek, M.,Burlacu, A., Rzeszotarski, D., Botezatu, N., Herghelegiu, P., Moldoveanu, F., Strumillo, P., Moldoveanu, A. Computer Vision for the Visually Impaired: the Sound of Vision System. IEEE International Conference on Computer Vision Workshops, pp. 1480-1489, 2017.

\bibitem{Csapo} Csap\'{o}, A., Wers\'{e}nyi, G., Nagy, H., Stockman, T. A survey of assistive technologies and applications for blind users on mobile platforms: a review and foundation for research. Journal on Multimodal User Interfaces. Vol. 9, issue 4,  pp. 275-286, 2015.

\bibitem{Poggi} Poggi, M., Mattoccia, S. A wearable mobility aid for the visually impaired based on embedded 3d vision and deep learning. Proceeding of IEEE Symposium on Compututers and Communication, pp. 208-213, 2016.

\bibitem{Zientara} Zientara, P.,A., Lee, S., Smith, G., H., Brenner, R., Itti, L., Rosson M., B., Carroll, J., M., Irick K., M., Narayanan, V. Third Eye: A shopping assistant for the visually impaired. Computer Vol. 50, Issue 2, pp. 16-24, 2017.

\bibitem{Owayjan} Owayjan, M., Hayek, A., Nassrallah, H., Eldor, M. Smart Assistive Navigation System for Blind and Visually Impaired Individuals. 2015 International Conference on Advances in Biomedical Engineering (ICABME), pp. 162-165, 2015.

\bibitem{Dunai} Dunai, L. D., Lengua, I. L., Tortajada, I., Brusola Simon, F. Obstacle detectors for visually impaired people. 2014 International Conference on Optimization of Electrical and Electronic Equipment (OPTIM),  pp. 809-816, 2014.

\bibitem{Kensing} Kensing, F., Simonsen, J., and B\o dker, K. MUST: A Method for Participatory Design. Hum-Comput Interact, vol. 13, no. 2, pp. 167-198, Jun. 1998.

\bibitem{Carroll} \noindent Carroll, J. M., Rosson, M. B. Participatory design in community informatics. Des. Stud., vol. 28, no. 3, pp. 243-261, May 2007.

\bibitem{Ren} Ren, Sh., He, K., Girshick, R., and Sun, J.  Faster R-CNN: Towards real-time object detection with region proposal networks. In Advances in neural information processing systems, pp. 91-99, 2015.

\bibitem{Liu} Liu, Ch., Mao, J., Sha, F., Yuille, A. Attention Correctness in Neural Image Captioning. Proceedings of the Thirty-First AAAI Conference on Artificial Intelligence, pp. 4176-4182, 2017.

\bibitem{Ohn-Bar}  Ohn-Bar, E., Kitani, K., Asakawa, Ch. Personalized Dynamics Models for Adaptive Assistive Navigation Interfaces. arXiv:1804.04118, [cs.LG], 2018.

\bibitem{Amos} Amos, B., Ludwiczuk, B., and Satyanarayanan, M. Openface:
A general-purpose face recognition library with mobile applications. Technical report, CMU-CS-16-118, CMU School of Computer Science, 2016.

\bibitem{Laina} Laina, I., Rupprecht, C., Belagiannis, V., Tombari, F., Navab, N. Deeper depth prediction with fully convolutional residual networks. Fourth International Conference on 3D Vision (3DV), pp. 239-248, 2016.

\bibitem{Valor} Varol, G., Laptev, I., Schmid, C. Long-Term Temporal Convolutions for Action Recognition.  IEEE Transactions on Pattern Analysis and Machine Intelligence. Vol. 40, issue 6, pp. 1510 - 1517, 2016.

\bibitem{Tensorflow}  Abadi M., Agarwal A., Barham P., Brevdo E., Chen Z., Citro C., Corrado G., Davis A., Dean J., Devin M., et al. TensorFlow: Large-Scale Machine Learning on Heterogeneous Distributed Systems, arXiv:1603.04467, 2016.

\bibitem{orcam} Orcam. MyEye 2.0. [Online]. Available from https://www.orcam.com 2018-10-16.

\bibitem{horus} Horus. Horus system. [Online]. Available from http://www.horus.tech 2018-10-16.

\bibitem{Verilook} Neurotechnology, VeriLook SDK. [Online]. Available from https://www.neurotechnology.com/verilook.html 2018-10-16.

>>>>

\bibitem{Bourne} R. R. A. Bourne et al. Vision Loss Expert Group. Magnitude, temporal trends, and projections of the global prevalence of blindness and distance and near vision impairment: a systematic review and meta-analysis. Lancet Glob Health. Vol. 5(9), pp. 888-897, 2017.

\bibitem{Caraiman} S. Caraiman et al. A. Computer Vision for the Visually Impaired: the Sound of Vision System. IEEE International Conference on Computer Vision Workshops, pp. 1480-1489, 2017.

\bibitem{Csapo} A. Csap\'{o}, G. Wers\'{e}nyi, H. Nagy, and T. A. Stockman. A survey of assistive technologies and applications for blind users on mobile platforms: a review and foundation for research. Journal on Multimodal User Interfaces. Vol. 9, issue 4,  pp. 275-286, 2015.

\bibitem{Poggi} M. Poggi and S. Mattoccia. A wearable mobility aid for the visually impaired based on embedded 3d vision and deep learning. Proceeding of IEEE Symposium on Compututers and Communication, pp. 208-213, 2016.

\bibitem{Zientara} P. A. Zientara at al. Third Eye: A shopping assistant for the visually impaired. Computer Vol. 50, Issue 2, pp. 16-24, 2017.

\bibitem{Owayjan} M. Owayjan, A. Hayek, H. Nassrallah, and M. Eldor. Smart Assistive Navigation System for Blind and Visually Impaired Individuals. 2015 International Conference on Advances in Biomedical Engineering (ICABME), pp. 162-165, 2015.

\bibitem{Dunai} L. D. Dunai, I. L. Lengua, I. Tortajada, and F. B. Simon. Obstacle detectors for visually impaired people. 2014 International Conference on Optimization of Electrical and Electronic Equipment (OPTIM),  pp. 809-816, 2014.

\bibitem{Kensing} F. Kensing, J. Simonsen, and K. B\o dker. MUST: A Method for Participatory Design. Human Computer Interaction, vol. 13, no. 2, pp. 167-198, Jun. 1998.

\bibitem{Carroll} J. M. Carroll and M. B. Rosson. Participatory design in community informatics. Des. Stud., vol. 28, no. 3, pp. 243-261, May 2007.

\bibitem{Ren} Sh. Ren, K. He, R. Girshick, and J. Sun.  Faster R-CNN: Towards real-time object detection with region proposal networks. In Advances in neural information processing systems, pp. 91-99, 2015.

\bibitem{Liu} Ch. Liu, J. Mao, F. Sha, and A. Yuille. Attention Correctness in Neural Image Captioning. Proceedings of the Thirty-First AAAI Conference on Artificial Intelligence, pp. 4176-4182, 2017.

\bibitem{Ohn-Bar} E. Ohn-Bar, K. Kitani, and Ch. Asakawa. Personalized Dynamics Models for Adaptive Assistive Navigation Interfaces. arXiv:1804.04118, [cs.LG], 2018.

\bibitem{Amos} B. Amos, B. Ludwiczuk, and M. Satyanarayanan. Openface:
A general-purpose face recognition library with mobile applications. Technical report, CMU-CS-16-118, CMU School of Computer Science, 2016.

\bibitem{Laina} I. Laina, C. Rupprecht, V. Belagiannis, F. Tombari, and N. Navab. Deeper depth prediction with fully convolutional residual networks. Fourth International Conference on 3D Vision (3DV), pp. 239-248, 2016.

%-------------------

\bibitem{Valor} G. Varol, I. Laptev, and C. Schmid. Long-Term Temporal Convolutions for Action Recognition.  IEEE Transactions on Pattern Analysis and Machine Intelligence. Vol. 40, issue 6, pp. 1510 - 1517, 2016.

\bibitem{Tensorflow} M. Abadi et al. TensorFlow: Large-Scale Machine Learning on Heterogeneous Distributed Systems, arXiv:1603.04467, 2016.

%-------------------

\bibitem{orcam} Orcam. MyEye 2.0. [Online]. Available from https://www.orcam.com [retrieved: 1 2019].

\bibitem{horus} Horus. Horus system. [Online]. Available from http://www.horus.tech [retrieved: 1 2019].

\bibitem{Verilook} Neurotechnology, VeriLook SDK. [Online]. Available from https://www.neurotechnology.com/verilook.html [retrieved: 1 2019].
